---
title: "Disney_Hotstar"
author: "Arindam Baruah"
date: "2023-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
```

```{r load_libraries}
library(tidyverse)
library(ggplot2)
library(tidyr)
library(kableExtra)
```


```{r read_data}

df_cred <- read_csv('data/credits.csv')
df_title <- read_csv('data/titles.csv')

head(df_cred)
head(df_title)

```

# What are we looking to answer ?

After going through a glimpse of the data, here are a few questions that will be addressed in the following study:

1. Temporal analysis of the number of releases for shows and movies over the years.
2. Movies/Shows with the largest cast members.
3. Have aggregated IMDB ratings changed over the years ?
4. Which countries have produced the most content ?
5. Popular genres over the years and their IMDB ratings.
6. Distribution of the runtime of the content.

```{r join_datasets}

df_joined <- merge(x=df_title,y=df_cred,by='id')
tail(df_joined)
```
```{r data_clean}
df_joined$production_countries <- df_joined$production_countries %>% str_sub(2,-2)

df_joined$genres <- df_joined$genres %>% str_sub(2,-2)

df_joined <- df_joined %>% select(-description)

df_joined$genres <- df_joined$genres %>% str_replace_all("'","")
df_joined$production_countries <- df_joined$production_countries %>% str_replace_all("'","")

df_title$production_countries <- df_title$production_countries %>% str_sub(2,-2)

df_title$genres <- df_title$genres %>% str_sub(2,-2)

df_title <- df_title %>% select(-description)

df_title$genres <- df_title$genres %>% str_replace_all("'","")
df_title$production_countries <- df_title$production_countries %>% str_replace_all("'","")


```


```{r Characters per movie}
df_count <- df_joined %>% 
  group_by(title) %>% 
  summarise(Number_of_characters= sum(n_distinct(person_id))) %>% 
  arrange(-Number_of_characters)

head(df_count,10) %>% 
  kable(caption = 'Number of actors in each movie',booktabs = TRUE) %>% 
kable_styling(bootstrap_options = c("bordered","hover")) #Creating a table


```
```{r releases by year}

df_releases <- df_title %>% group_by(release_year,type) %>%
  summarise(Releases=n())

head(df_releases)

```


